\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) Event (compact-binary mergers) Rate calculator and simulator

### 2024-06-20 paper/paper.tex
mac

  \begin{itemize}
  \tightlist
  \item
    For the unlensed events, The sampling distribution
    \((\,R_m(z_s)\,)\) for the source's redshift \((\,z_s\,)\) is
    derived from the merger rate density of compact binaries, which, in
    turn, is based on the star formation rate. The code is meticulously
    designed to enable the straightforward integration of future updates
    or user-specified distributions of these sources.
  \item
    Intrinsic and extrinsic parameters \((\theta)\) of GW sources are
    sampled using prior distributions \((P(\theta))\) from the gwcosmo
    (gwcosmo Contributors 2022) and bilby (\textbf{Ashton2019?})
    packages, with options for users to input custom distributions.
  \end{itemize}
\item
  Sampling of lens galaxies attributes and source red-shifts:

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-astropy}
Astropy Collaboration. 2013. {``{Astropy: A community Python package for
astronomy}.''} \emph{Astronomy and Astrophysics} 558 (October).
\url{https://doi.org/10.1051/0004-6361/201322068}.

>>>>

  \begin{itemize}
  \tightlist
  \item
    For the unlensed events, The sampling distribution
    \((\,R_m(z_s)\,)\) for the source's redshift \((\,z_s\,)\) is
    derived from the merger rate density of compact binaries, which, in
    turn, is based on the star formation rate. The code is meticulously
    designed to enable the straightforward integration of future updates
    or user-specified distributions of these sources.
  \item
    Intrinsic and extrinsic parameters \((\theta)\) of GW sources are
    sampled using prior distributions \((P(\theta))\) from the gwcosmo
    (gwcosmo Contributors 2022) and bilby (Ashton et al. 2019) packages,
    with options for users to input custom distributions.
  \end{itemize}
\item
  Sampling of lens galaxies attributes and source red-shifts:

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Ashton2019}
Ashton, Gregory, Moritz Hübner, Paul D. Lasky, Colm Talbot, Kendall
Ackley, Sylvia Biscoveanu, Qi Chu, et al. 2019. {``Bilby: A
User-Friendly Bayesian Inference Library for Gravitational-Wave
Astronomy.''} \emph{The Astrophysical Journal Supplement Series} 241
(2): 27. \url{https://doi.org/10.3847/1538-4365/ab06fc}.

\bibitem[\citeproctext]{ref-astropy}
Astropy Collaboration. 2013. {``{Astropy: A community Python package for
astronomy}.''} \emph{Astronomy and Astrophysics} 558 (October).
\url{https://doi.org/10.1051/0004-6361/201322068}.
